
Humanoid robot soccer is a very traditional competitive task that aims to push boundaries of state-of-the-art in robotics. One of the many challenges of playing soccer is kicking a ball efficiently, according to each context during the game. Besides, we have been witnessing the improvement in modern Deep Reinforcement Learning (DRL) techniques towards the goal of learning complex continuous control problems such as locomotion and several others movements present in robotics. Model-free DRL is a Machine-Learning field that combines Deep Learning (DL) methods with Reinforcement Learning (RL) algorithms, and greatly fit robotics locomotion problems since it avoids dealing with the complex dynamics of a humanoid robot. In this work, we focused on a particular problem of the humanoid robot soccer domain which consists in teaching the robot to kick a ball towards a final planned distance, with the purpose of passing the ball to other teammates. This document first gives a presentation of the given problem, with the related works and proposed approach, followed by an introduction of some background concerning RL and DL, including a summarized description of some cutting-edge DRL techniques. In the next chapters, it presents the tools we used, along with the proposed models to the problem, followed by the description of the experiments and the obtained results. Finally, it presents a conclusion with the future works to be developed.


%In the future, we plan to achieve a full behavior for the intended action, by using DRL techniques in first learning an initial behavior, using imitation learning on an already built kick movement, and then learning how to achieve the ultimate goal of reaching a desired final distance for the ball.